---
title: "The Exchange Rate of the Japanese Yen and the United States Dollar Pre SARS-CoV-2  vs. During SARS-CoV-2 "
author: "Kizuku Miyashita & Cameron Lee"
date: "4/29/2022"
output:
  html_document: default
  pdf_document: default
---
<br>
<h2>
Abstract
</h2>

In the study we conducted, we wanted to see if there was a correlation between the value of the Japanese Yen's exchange rate with the United States dollar before the SARS-CoV-2 
virus became a worldwide pandemic and its current value as the pandemic is ongoing.  
<br>


<h2>
SARS-CoV-2 Trends In Japan
</h2>

Here is a graph representing the number of monthly Japan has had since 2020. 

<!--#Kizuku's code
#Plot of covid trends in Japan-->
```{r}

library(xlsx)
dataJ = read.xlsx("JapanCovidTrends.xlsx",sheetIndex = 1, header = T)
monthJ = dataJ[,1]
caseJ = dataJ[,2]
plot(monthJ,caseJ,main="Covid Cases vs Date in JP",
     xlab = "Date (Monthly)",ylab="New Cases",
     type = "o", col='blue')
```

The graph details a significant number of cases in Japan during this worldwide
pandemic.  

<br>




<h2>
SARS-CoV-2 Trends in the United States
</h2>

<!--##Plot of COVID trends in USA-->

```{r}

dataUSA = read.xlsx("USACovidTrends.xlsx",sheetIndex = 1, header = T)
dataUSA
monthUSA = dataUSA[,1]
caseUSA = dataUSA[,2]
summary(caseUSA)
plot(monthUSA,caseUSA,main="Covid Cases vs Date in USA",
     xlab = "Date (Monthly)",ylab="New Cases (In Hundreds)",
     type = "o", col='blue')
```


As you can see, there is a much larger spike in the number of cases in the United States.

<br>

<!--


#COMMENT
#Explaining our hypothesis
#Explaining how we conducted our research 
```
-->

<h2>
Hypothesis Testing 
</h2>

Due to the economic turmoil that the SARS-CoV-2 virus caused, it could be assumed that
the monetary value of the Yen, when exchanged with the U.S. Dollar, had a higher value prior to the illness spreading globally.

To test our hypothesis, we conducted three pooled-t tests. As both data sets that we collected had almost equal standard deviations, we could go forward with this test. 

<i><b>Significant Note: The lesser the numeric value of the Yen, the higher the value when exchanged with the United States Dollar </b></i>


<h3> Two-Tailed Pooled T-Test </h3>

First, we performed a two-tailed pooled t-test to decide whether or not there was sufficient enough data to reject the claim that the exchange rate from both time periods were equal.

<br>

Here is our code:
<!--#Hypothesis Testing Two means (Two-Tailed)-->
```{r}
data = read.xlsx("ExchangeRateData.xlsx",sheetIndex = 1, header = T)
data
monPreCOVID = data[seq(1,36), 1]
monPreCOVID
monDurCOVID = data[seq(37,63),1]
preCOVID = data[seq(1,36), 2]
preCOVID
duringCOVID = data[seq(37,63),2]
t.test(preCOVID, duringCOVID, mu = 0, var.equal = T, alternative = "two.sided", conf.level = 0.95)
p = 0.07258
```

In this study, we assumed that the average exchange rate from pre-covid times compared 
covid times were not equal. Since p = 0.07258, it is greater than 0.05 which means we 
cannot reject the claim that the null hypothesis are equal to each other. 

Although we cannot reject the null hypothesis, our p-value provides us with insight that we may be able to use another t-test to see what time period had the greater exchange rate value. This is because p is near our rejection value of 0.05 for our data.

Due to the results of our first test, we must do a right-tailed and left-tailed pooled t-test as we are unable to reject null hypothesis.
<br>

<h3> Left-Tailed Pooled T-Test </h3>
Secondly, we ran a left-tailed pooled t-test to see if the average exchange rate before covid was greater during covid.

Here is our code:
<!--#Hypothesis Testing Two means (Left-Tailed)-->
```{r}
t.test(preCOVID, duringCOVID, mu = 0, var.equal = T, alternative = "less", conf.level = 0.95)
p = 0.9637
```
In this study, we assumed that the average exchange rate from pre-covid times were greater compared to covid times. Since p = 0.9637, it is greater than 0.05 which means we cannot reject the null hypothesis. There is no evidence against the null hypothesis, therefore the test is inconclusive for the data in our study and proves our initial assumptions were incorrect. 
<br>

<h3> Right-Tailed Pooled T-Test </h3>
Lastly, we decided to construct a right-tailed pooled t-test to rule out the idea that we can reject the null hypothesis. 

Here is our code:
<!--#Hypothesis Testing Two means (Right-Tailed)-->
```{r}
t.test(preCOVID, duringCOVID, mu = 0, var.equal = T, alternative = "greater", conf.level = 0.95)
p = 0.03629
```
In this study, we assumed that the average exchange rate from pre-covid times were less compared to covid times. Since p = 0.03629, it is less than 0.05 which means we can reject the null hypothesis.

With 95% confidence, the Japanese Yen's numeric value is greater during pre-covid times compared to present day covid times. Ultimately, this means that the exchange rate was less during before covid started when comparing it to the present exchange rates. 
<br>

 
<h2> Conclusion </h2>
We can conclude from our last t-test that the value of the Japanese Yen has been greater during covid times when being compared to pre-covid times. Although it was assumed that the value of the Yen would be greater during non-covid times, it has been proven false and remains in a more positive state. Our original assumption was proven untrue. 
<br>
<br>
<br>

<h2> Predictions For Future Exchange Rate Values </h2>

After discovering that our initial hypothesis was incorrect, we decided upon conducting research to see if we could attain 
the exchange rate for the Japanese Yen for the month of January in 2024.

<h3> Pre-Covid and During Covid Exchange Rates </h3>

Before getting into our predictions for the January of 2024, here are the graphs describing the exchange rates before the pandemic and during the pandemic. 

<!--#Pre-Covid Exchange Rates
#Making Exchange Rate Plot-->

```{r}
plot(monPreCOVID, preCOVID, main = "JPY Per USD Exchange Rates Before COVID", xlab = "Months", 
     ylab = "JPY (짜)", col = "Blue", type = "b")

#During-Covid Exchange Rates
plot(monDurCOVID,duringCOVID, main = "JPY Per USD Exchange Rates During COVID", xlab = "Months", 
     ylab = "JPY (짜)", col = "Red", type = "b")
```

As you can see from the 2017-2020 graph, there is a very unstable exchange rate between the Japanese Yen and the United States dollar. Every month there is a rapid fluctuation or decrease in the value of the Yen. 

The 2020-2022 year graph provides evidence there is a clear increase in value at the start of COVID and then a tremendous decrease of value that continues to reflect the present day value. 
<br>




<h3> Linear Regression to Predict January of 2024 </h3>

As we looked at the data we contained, we disregarded any data before 2021 as it was not current and did not allow for us to make a proper linear regression line. 

Using the data from 2021-present, we had to make sure that there was no identifiable residual pattern and confirm that the data follows a normal line. 

We checked to see if these requirements were true by using a matrix plot of the linear regression line that we created. 

Here is our code:

<!--Normal Graph-->
```{r}

x_date = c(0:14)
y_exchange = data[seq(49,63,1),2]

m = lm(formula = y_exchange~x_date)
summary(m)

#checking if it's okay to use linear regression.
layout(matrix(data=1:4,nrow=2,ncol=2,byrow=T))
plot(m)
layout(matrix(data=1,nrow=1,ncol=1))#reset

```

The top two graphs are the ones that we mainly focused on. 

The top-left graph is the residual graph. We concluded that there was no indication of a pattern that would compromise our study. As for the normal qqline plot, data values followed the line very closely and did not stray far. Due to these graphs passing the requirements we were able to use the regression line we created to compute our exchange rate prediction for the month of January 2024. 

<br>

Here is our code to predict the month of January 2024:
```{r}
y.intercept=m$coefficients[1]
slope=m$coefficients[2]
cat("y-intercept = ", y.intercept,"\t","slope = ", slope, "\n")
cat("The regression equation: $1 = ",y.intercept," + (",slope,") * Number_of_months (JPY)\n")

#Plotting
plot(x_date,y_exchange,main="Exchange rate JPY-USD",
     xlab = "Date (Monthly)",ylab="JPY (짜)",
     pch = 16,col='blue')
abline(reg = m,col="red")

#2024
cat("$1 = ",y.intercept + slope * 48, "(JPY)\n")
```

Our prediction is based off of the assumption that the data will stay in this linear progression. If the trajectory is matching to what we have projected, the exchange rate from the Japanese Yen to the U.S. Dollar will amount to 짜145.2162 to $1. 
<br>
<br>
<br>







